---
output: github_document
bibliography: simbib.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Reproduce the Analysis from @gerard2021double

## Instructions

1. Install the appropriate R packages

    ```{r, eval = FALSE}
    install.packages(c("devtools",
                       "tidyverse",
                       "ggthemes",
                       "latex2exp"))
    devtools::install_github("dcgerard/hwep")
    devtools::install_github("dcgerard/phwelike")
    ```
    
    The hwep package contains the new methods from @gerard2021double, while the phwelike package contains the code written by @jiang2021computational and placed in package form by me.

2. Run `make` in the terminal.

## Other Files

- [alpha_tetra.nb](./analysis/alpha_tetra.nb) is a Mathematica
  notebook that solves for the double reduction parameter given the
  gamete genotype frequencies in a tetraploid population at HWE. 
  This file was used to derive Equation (XYZ) in @gerard2021double.
  The segregation probabilities come from Table 9 of @fisher1943inheritance.
  
## Session Information

```{r, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
lapply(c("devtools",
         "tidyverse",
         "ggthemes",
         "latex2exp",
         "hwep",
         "phwelike"), 
       FUN = library,
       character.only = TRUE)
```

```{r, echo = FALSE, comment=""}
sessionInfo()
```

# References
