---
output: github_document
bibliography: simbib.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Reproduce the Analysis from @gerard2021double

[![NSF-2132247](https://img.shields.io/badge/NSF-2132247-blue.svg)](https://nsf.gov/awardsearch/showAward?AWD_ID=2132247)

This repo contains the scripts and instructions to reproduce the results of @gerard2021double. This involves simulations and real data analyses using the data from @shirasawa2017high (<http://sweetpotato-garden.kazusa.or.jp/>) and @delomas2021genotyping ([doi:10.5061/dryad.crjdfn33r](https://www.doi.org/10.5061/dryad.crjdfn33r)).

## Instructions

To run these scripts, you will need to have the latest version of R, GNU Make, wget, and 7-zip, running on a Linux system.

1. Install the appropriate R packages

    ```{r, eval = FALSE}
    install.packages(c("devtools",
                       "tidyverse",
                       "ggthemes",
                       "latex2exp",
                       "BiocManager",
                       "future"))
    BiocManager::install("VariantAnnotation")
    devtools::install_github("dcgerard/hwep")
    devtools::install_github("dcgerard/phwelike")
    devtools::install_github("dcgerard/updog")
    ```
    
    The `{hwep}` package contains the new methods from @gerard2021double, while the `{phwelike}` package contains the code written by @jiang2021computational and placed in package form by me.

2. Run `make` in the terminal.

## Other Files

- [alpha_tetra.nb](./analysis/alpha_tetra.nb) is a Mathematica
  notebook that solves for the double reduction parameter given the
  gamete genotype frequencies in a tetraploid population at equilibrium. 
  The segregation probabilities come from Table 9 of @fisher1943inheritance.
- [hex_equi.nb](./analysis/hex_equi.nb) is a Mathematica notebook that
  calculates gamete frequencies at equilibrium for hexaploids.
- [diploid.nb](./analysis/diploid.nb) is a Mathematica notebook that
  explores the $U$-statistic approach to testing for equilibrium in 
  diploids.
  
## Session Information

```{r, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
lapply(c("devtools",
         "tidyverse",
         "ggthemes",
         "latex2exp",
         "hwep",
         "phwelike",
         "BiocManager",
         "VariantAnnotation",
         "future",
         "updog"), 
       FUN = library,
       character.only = TRUE)
```

```{r, echo = FALSE, comment=""}
sessionInfo()
```

## Acknowledgments

This material is based upon work supported by the National Science Foundation under Grant No. [2132247](https://www.nsf.gov/awardsearch/showAward?AWD_ID=2132247). The opinions, findings, and conclusions or recommendations expressed are those of the author and do not necessarily reflect the views of the National Science Foundation.

# References
